The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-04 papers/pair-correlation/paper.tex
Added abcd, etc. to figures in pair paper. Tested on paho-arch. Took 0:49.00.

\begin{figure*}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.1$.}
    \label{fig:pair-distribution-1}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.3$.}
    \label{fig:pair-distribution-3}
  \end{subfigure}
  \caption{ \paircaption \fixme{Do we want to label the y-axis for the
      1d plots? } \davidsays{I think so... also add a) b) c) d)}
  }\label{fig:pair-distribution}
\end{figure*}

@@

We begin by examining the pair distribution function near a hard wall,
with a focus on the case where one of the two spheres is in contact
with the hard wall.  Figure~\ref{fig:pair-distribution-1}a
and~\ref{fig:pair-distribution-3}a compare the results of our
approximate functional with Monte Carlo simulation at packing
fractions of 0.1 and 0.3 respectively.  We see reasonable agreement at
the lower density, with some reduced oscillations at larger distances,
and a flatter angular dependence when the two spheres are in contact.
At the higher density, we see significant structure developing in the
simulation results that is not reflected in our approximation.

Figure~\ref{fig:pair-distribution-1}b
and~\ref{fig:pair-distribution-3}b show the pair distribution function
as plotted along a path illustrated in
Fig.~\ref{fig:pair-distribution-1}a.  These plots compare this work
with Monte Carlo results, as well as the approximations of Sokolowski
and Fischer~\cite{sokolowski1992role} and that of Fischer and
Methfessel~\cite{fischer1980born} at packing fractions of 0.1 and 0.3.
The approach of Fischer and Methfessel is only defined when the two
spheres are in contact, and is therefore only plotted on that segment
of the path.  As an input to both previous approximations we use the
hard sphere radial distribution function found with Monte Carlo
simulation, interpolated as necessary.  We find that both previous
approximations to the pair distribution function predict the
qualtitative angular dependence of the pair distribution function at
contact better than this work.  However, in each case the pair
distribution function has a systematic error at contact---either too
high or too low.  Thus while our approximation is smoother than either
of the existing approaches, its errors will have a tendancy to cancel
when used in a perturbation expansion.  At higher densities, the
approximation of Fischer and Methfessel requires evaluating the radial
distribution function at densities significantly higher than the
freezing density, which poses numerical difficulties when using the
radial distribution function from simulation.  When the two points are
more than a radius away from contact, we find that any of these
approaches gives a reasonable prediction, with our approach
underestimating the oscillations in $g^{(2)}$, as expected based on the
fit in Fig.~\ref{fig:radial-distribution}.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Tweak spacing, add a, b, c, etc. The 1d plots still
      have two curves for this work, do we want to remove one?
      \davidsays{I'm not sure, I might be tempted to keep both,
        although if we do we should explain the difference between
        them. (left-right mirror image)}} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}

>>>>

\begin{figure*}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}
    \vspace{-0.6cm}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
    \vspace{-0.6cm}
  \end{subfigure}
  \caption{\paircaption}
  \label{fig:pair-distribution}
\end{figure*}

@@

We begin by examining the pair distribution function near a hard wall,
with a focus on the case where one of the two spheres is in contact
with the hard wall.  Figure~\ref{fig:pair-distribution}a
and~\ref{fig:pair-distribution}a compare the results of our
approximate functional with Monte Carlo simulation at packing
fractions of 0.1 and 0.3 respectively.  We see reasonable agreement at
the lower density, with some reduced oscillations at larger distances,
and a flatter angular dependence when the two spheres are in contact.
At the higher density, we see significant structure developing in the
simulation results that is not reflected in our approximation.

Figure~\ref{fig:pair-distribution}b
and~\ref{fig:pair-distribution}b show the pair distribution function
as plotted along a path illustrated in
Fig.~\ref{fig:pair-distribution}a.  These plots compare this work
with Monte Carlo results, as well as the approximations of Sokolowski
and Fischer~\cite{sokolowski1992role} and that of Fischer and
Methfessel~\cite{fischer1980born} at packing fractions of 0.1 and 0.3.
The approach of Fischer and Methfessel is only defined when the two
spheres are in contact, and is therefore only plotted on that segment
of the path.  As an input to both previous approximations we use the
hard sphere radial distribution function found with Monte Carlo
simulation, interpolated as necessary.  We find that both previous
approximations to the pair distribution function predict the
qualtitative angular dependence of the pair distribution function at
contact better than this work.  However, in each case the pair
distribution function has a systematic error at contact---either too
high or too low.  Thus while our approximation is smoother than either
of the existing approaches, its errors will have a tendancy to cancel
when used in a perturbation expansion.  At higher densities, the
approximation of Fischer and Methfessel requires evaluating the radial
distribution function at densities significantly higher than the
freezing density, which poses numerical difficulties when using the
radial distribution function from simulation.  When the two points are
more than a radius away from contact, we find that any of these
approaches gives a reasonable prediction, with our approach
underestimating the oscillations in $g^{(2)}$, as expected based on the
fit in Fig.~\ref{fig:radial-distribution}.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for this
      work} The triplet distribution function $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at
    packing fraction 0.3, plotted when $\rr_1$ and $\rr_2$ are in contact.  The
    color plot on the left shows the triplet distribution function, with white
    corresponding to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path shown as a
    dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}
